Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-06-13 snapshot_system/failover.tex
merge
Added some initial data files for block<-snapshot links, and a couple paragraphs to failover.tex on how the empirical results support the model.

\subsection{Fault Analysis }

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{shared.pdf}
\caption{Assoication of data blocks to VMs.}
\label{fig:shared}
\end{figure}

@@

>>>>

\subsubsection{Fault Analysis }

@@

\comments{
\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{shared.pdf}
\caption{Assoication of data blocks to VMs.}
\label{fig:shared}
\end{figure}
}

@@

\subsection{Empirical Validation}
To validate our theoritical model for the probability of data loss, we computed
the number of VMs using each block in a global index for the 350 VM traces.
As you can see in Fig.~\ref{??}, The average number of VMs sharing a block
%TODO: insert figure generated from data/links_no_cds.dat
increases linearly with the number of snapshots. For 350 snapshots there are an
average of 13.1 links to a given block in the global index.
%What else do we need from the simulation to validate the model?

\subsubsection{CDS and Fault Tolerance}
%all numbers in this paragraph need to be corrected after I re-run the tests
%using the actual cds generator code
As part of our emprirical validation of our model, we also computed the effects
of the CDS on fault tolerance. If we exclude the top 5\% most popular blocks
and set aside those in the CDS, the average number of links to a non-CDS block
%TODO: insert figure generated from data/links_cds.dat and data/links_wo_cds.dat
drops to 10.3 for 350 snapshots. This means that on average, \~3 fewer
snapshots will be affected by a lost data block in the general data store.
The average number of links to a CDS block however, for 350 snapshots, is
65.7. This suggests that a much higher replication factor is warranted for
the CDS, as on average, a CDS block appears in 19\% of all the snapshots.

The CDS gives a clear boundary for setting different replication factors,
And our tests suggest that by separating the replication factor for the CDS
and non-CDS blocks, greater fault tolerance can be acheived.
